---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- Generate with R -e 'rmarkdown::render("README.Rmd")' -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gcvt

Work in progress (imagine a web1.0 yellow roadwork sign here).

The goal of gcvt is to provide data and functions for visualising
    road networks. Specifically it is focussed on the TEN-T European
    road network.

## Installation

You can install gcvt from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("IntegratedTransportPlanning/gcvt")
```

## Apps

This repo contains a number of shiny apps that view our data in different ways. The two most developed are `combined_viewer_mapbox` and `combined_viewer_leaflet`.

The leaflet version is currently less buggy. The mapbox version has link offsetting (so you can see the direction of links).

To run the apps locally use:

```{r, eval=FALSE}
shiny::runApp("R/combined_viewer_leaflet/")
```

### Mapbox app

The mapbox app requires some additional setup:

```{sh}
cd R/combined_viewer_mapbox
npm install
npm run build
```

I run the app like so, you can run it from rstudio if you prefer:

```{sh, eval=FALSE}
R -e 'shiny::runApp(".", port=6619)'
```
